TGI-spinal-power

### 2023-06-15 old/tgispine_hypotheses.Rmd
more shuffling

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:60) {
  df <- simulate_subj(i, 0, 1)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

# model summaries
summary(model.cold)
summary(model.warm)

>>>>

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:30) {
  df <- simulate_subj(i, 0, 1)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

# model summaries
summary(model.cold)
summary(model.warm)
```

# next, run model checks

```{r}
# first check cold
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```
```{r}
# then check warm
model.warm.assmup <- simulateResiduals(model.warm, n = 1000)
plot(model.warm.assmup)
```

### 2023-06-15 old/tgispine_og-plots-exp1.Rmd
more shuffling

# summary
df_nmedian <- aggregate(list(cold = df_norm$ncold, warm = df_norm$nwarm, pain = df_norm$npain), 
                        by = list(id = df_norm$id, dermatome = df_norm$dermatome, 
                                  location_cold = df_norm$location_cold), FUN = median)
```
# Analysis and effect sizes
```{r}
# cold ratings anova
cold_anova <- ezANOVA(
  data = df_nmedian
  , dv = .(cold)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

# cold ratings linear mixed model
# warm ratings anova
warm_anova <- ezANOVA(
  data = df_nmedian
  , dv = .(warm)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

>>>>

# summary
df_nmedian <- aggregate(list(cold = df_norm$ncold, warm = df_norm$nwarm, pain = df_norm$npain), 
                        by = list(id = df_norm$id, dermatome = df_norm$dermatome, 
                                  location_cold = df_norm$location_cold, arm = df_norm$location_arm),
                        FUN = median)
# divide by arm location
df_upper <- df_nmedian[df_nmedian$arm == 'upperarm' ,]
df_fore <- df_nmedian[df_nmedian$arm == 'forearm' ,]
```
# Analysis and effect sizes
```{r}
# cold ratings anova
coldu_anova <- ezANOVA(
  data = df_upper
  , dv = .(cold)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

coldf_anova <- ezANOVA(
  data = df_fore
  , dv = .(cold)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

# cold ratings linear mixed model
# warm ratings anova
warmu_anova <- ezANOVA(
  data = df_upper
  , dv = .(warm)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

warmf_anova <- ezANOVA(
  data = df_fore
  , dv = .(warm)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

### 2023-06-15 tgi-compiler.Rmd
more shuffling

---
title: "TGI Spinal Analysis Code Experiment 1"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

@@

# Loading data
```{r data, echo = FALSE}
# Extract all .csv files and compile
filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
# empty dataframes for data
## with new data trials file will have changed to include temperature coding!
df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
test <- merge(df_res, df_demo)

# save new data-frame
fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
write.csv(df_res, fileName, row.names = FALSE)

@@

# correlate
qual_cor <- hetcor(df_corr, type = 'pearson')
cormat <- qual_cor$correlations

# significance values
p <- cor.mtest(df_corr, type ='pearson')$p

@@

# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,3], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cw_plot

ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,5], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cb_plot

ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[3,5], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_wb_plot

# combine non TGI
CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
                           nrow = 1, ncol = 3,
                           labels = c('A','B','C'))
CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
                                 top = text_grob("Non-TGI", 
                                                 size = 12))

# TGI plots
ggplot(df_corr, aes(x = TGIcold, y = TGIwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[2,4], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> TGI_cw_plot

ggplot(df_corr, aes(x = TGIcold, y = TGIburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[2,6], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> TGI_cb_plot

ggplot(df_corr, aes(x = TGIwarm, y = TGIburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[4,6], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> TGI_wb_plot

# combine TGI
TGI_corr_plot <- ggarrange(TGI_cw_plot, TGI_cb_plot, TGI_wb_plot,
                           nrow = 1, ncol = 3,
                           labels = c('D','E','F'))
TGI_corr_plot <- annotate_figure(TGI_corr_plot, 
                                 top = text_grob("TGI", 
                                                 size = 12))

@@

ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
       width = 14, height = 9, dpi = 1000)
```

>>>>

---
title: "TGI Spinal Data Compiler"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

To compile all the raw data, need to access paths in directory
This is done for experiment 1 first, then experiment 2

@@

# EXPERIMENT 1 DATA
```{r data, echo = FALSE}
# Extract all .csv files and compile
filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
# empty dataframes for data
## with new data trials file will have changed to include temperature coding!
df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_exp1_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
df_res <- merge(df_res, df_demo)
df_res <- df_res %>% 
  select(-c(warmT, coldT, Tested, Calibration, Notes))

# save new data-frame
write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)

@@

# correlate
qual_cor <- hetcor(df_corr, type = 'spearman')
cormat <- qual_cor$correlations

# significance values
p <- cor.mtest(df_corr, type ='spearman')$p

@@

# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,3], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> CNT_cw_plot

ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,5], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> CNT_cb_plot

ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[3,5], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> CNT_wb_plot

# combine non TGI
CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
                           nrow = 1, ncol = 3,
                           labels = c('A','B','C'))
CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
                                 top = text_grob("Non-TGI", 
                                                 size = 14))

# TGI plots
ggplot(df_corr, aes(x = TGIcold, y = TGIwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[2,4], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> TGI_cw_plot

ggplot(df_corr, aes(x = TGIcold, y = TGIburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[2,6], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> TGI_cb_plot

ggplot(df_corr, aes(x = TGIwarm, y = TGIburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[4,6], 2))),
            x=78, y=91, size = 5) +
  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-10,100) +
  theme_bw() +
  theme(axis.title = element_text(size = 12)) -> TGI_wb_plot

# combine TGI
TGI_corr_plot <- ggarrange(TGI_cw_plot, TGI_cb_plot, TGI_wb_plot,
                           nrow = 1, ncol = 3,
                           labels = c('D','E','F'))
TGI_corr_plot <- annotate_figure(TGI_corr_plot, 
                                 top = text_grob("TGI", 
                                                 size = 14))

@@

ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
       width = 10, height = 6.5, dpi = 1000)
```

### 2023-06-15 tgi-spinal_analysis-exp1.Rmd
more shuffling

---
title: "TGI Spinal Data Compiler"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

To compile all the raw data, need to access paths in directory
This is done for experiment 1 first, then experiment 2

@@

# EXPERIMENT 1 DATA
```{r data, echo = FALSE}
# Extract all .csv files and compile
filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
# empty dataframes for data
## with new data trials file will have changed to include temperature coding!
df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_exp1_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
df_res <- merge(df_res, df_demo)
df_res <- df_res %>% 
  select(-c(warmT, coldT, Tested, Calibration, Notes))

# save new data-frame
write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)

# check we have 40 participants with 96 trials
id_check <- count(df_res, 'ID')
id_check
```

>>>>

---
title: "TGI Spinal Analysis Code Experiment 1"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

@@

# Loading data
```{r data, echo = FALSE}
# Extract all .csv files and compile
filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
# empty dataframes for data
## with new data trials file will have changed to include temperature coding!
df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_exp1_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
test <- merge(df_res, df_demo)

# save new data-frame
fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
write.csv(df_res, fileName, row.names = FALSE)

# check we have 40 participants with 96 trials
id_check <- count(df_res, ID)
id_check
```

### 2023-06-15 tgispine_zoib_power-sim.Rmd
more shuffling

# Proportion zero function
Replaces proportion of data with zero, based on proportions for each condition calculated from pilot data - used in the simulation
```{r}
set.seed(326) #is this needed?
prop_zero <- function(x, vas = c('cold','warm','burn')) {
  x2 <- data.frame()
  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .05
  r <- rnorm(2, mean=0, sd=.05)
  if (vas[1] == 'cold'){
    x1 <- x %>%  filter(quality == 'cold')
    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
    zp_cnt <- CNTc_zero$prop[2] + r[1] 
    zp_tgi <- TGIc_zero$prop[2] + r[2]
    # adding if loop to make sure zp does not reach 0
    if (isTRUE(zp_cnt < 0)){
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)){
      zp_tgi = 0
    }
    # turn zp into the proportion of total columns
    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))

    # isolate TGI and non-TGI
    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
    x_tgi <- x1 %>% filter(stimuli == 'tgi')
    # finally, replace a proportion of the data with zeros! 
    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0

@@

  } else if (vas[1] == 'warm'){
    x1 <- x %>%  filter(quality == 'warm')
    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each       participant
    zp_cnt <- CNTw_zero$prop[2] + r[1] 
    zp_tgi <- TGIw_zero$prop[2] + r[2]
    # adding if loop to make sure zp does not reach 0
    if (isTRUE(zp_cnt < 0)){
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)){
      zp_tgi = 0
    }
    # turn zp into the proportion of total columns
    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
    # isolate TGI and non-TGI
    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
    x_tgi <- x1 %>% filter(stimuli == 'tgi')
    # finally, replace a proportion of the data with zeros! 
    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0

  } else if (vas[1] == 'burn') {
    x1 <- x %>%  filter(quality == 'burn')
    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
    zp_cnt <- CNTb_zero$prop[2] + r[1] 
    zp_tgi <- TGIb_zero$prop[2] + r[2]
    # adding if loop to make sure zp does not reach 0
    if (isTRUE(zp_cnt < 0)){
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)){
      zp_tgi = 0
    }
    # turn zp into the proportion of total columns
    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))

    # isolate TGI and non-TGI
    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
    x_tgi <- x1 %>% filter(stimuli == 'tgi')
    # finally, replace a proportion of the data with zeros! 
    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0

    #compile both data-sets again
    x2 <- rbind(x_cnt, x_tgi)
  }
  return(x2)
}
```

@@

## SIMULATIONS ##
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
po_b <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)

>>>>

# Proportion zero function
Replaces proportion of data with zero, based on proportions for each condition calculated from pilot data - used in the simulation
```{r}
set.seed(326) #is this needed?
prop_zero <- function(x, vas) {
  # check if a correct vas parameter is provided
  if (!vas %in% c("cold", "warm", "burn")) {
    stop("Only cold / warm / burn parameters allowed", .call = TRUE)
  }
  if (length(vas) > 1) {
    stop("VAS parameter should have length = 1", .call = TRUE)
  }

  # sellect subset of x
  x1 <- x %>%  filter(quality == vas)

  # sellect dfs with info about zero proportions
  # switch function allows to select a value based on a condition
  # a statement specified as the first parameter may be tested for many conditions # nolint
  # conditions are specified as the next arguments
  # returned value for a contition is given after = sign
    df_CNT <- switch(vas,
    cold = CNTc_zero,
    warm = CNTw_zero,
    burn = CNTb_zero)
    df_TGI <- switch(vas,
    cold = TGIc_zero,
    warm = TGIw_zero,
    burn = TGIb_zero)

    # get info abut zero proportion and add some variablity
    # first randomly generate two numbers around a normal distribution of 0,
    # with a standard deviation of .05
    r <- rnorm(2, mean=0, sd=.05)
    # then retrieve the relevant data and add generated random number
    zp_cnt <- df_CNT$prop[2] + r[1]
    zp_tgi <- df_TGI$prop[2] + r[2]
    # make sure that zp does not reach 0
    if (isTRUE(zp_cnt < 0)) {
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)) {
      zp_tgi = 0
    }

    # isolate TGI and non-TGI
    x_cnt <- x1 %>% filter(stimuli == "non-tgi")
    x_tgi <- x1 %>% filter(stimuli == "tgi")

    # turn zp into the number of total columns
    zp_cnt <- round(zp_cnt * nrow(x_cnt))
    zp_tgi <- round(zp_tgi * nrow(x_tgi))

    # finally, replace a proportion of the data with zeros!
    x_cnt$rating[sample(nrow(x_cnt), zp_cnt)] <- 0
    x_tgi$rating[sample(nrow(x_tgi), zp_tgi)] <- 0

@@

    return(x2)
}
```

@@

## SIMULATIONS
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
po_b <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)
